Title

### 2014-07-23 paper.tex

After the 320 sample comments have been labeled,
they are scored based on the number of ``yes'' given to the sample.
The table below shows the distribution of scores for the training data.

\begin{center}
\begin{tabular}{|r|r|}
\hline
\bfseries Score & \bfseries Count \\
\hline
0 & 87 \\ 1 & 60 \\ 2 & 51 \\ 3 & 122 \\
\hline
\end{tabular}
\end{center}

% corpus size and other statistics

\subsection{Studied Project and Data set}
\subsection{RQ1: Can we identify useful and useless discussion in code review?}
\subsection{RQ2: How impact of useless discussion impact to the software quality?}

>>>>

After the 320 sample comments have been labeled,
they are scored based on the number of ``yes'' given to the sample.
There were 87, 60, 51, and 122 comments with scores of 0, 1, 2, and 3, respectively.

After the similarity and distance metrics have been calculated,
these metrics appear to be able to separate the useful comments from the non-useful ones,
as can be seen in Fig.\ref{fig:scatter}.
Note that many comments have a cosine similarity metric of 0.
This is because the comment text and the corresponding commit message has no word in comment.

\begin{figure}[h]
\centering
\includegraphics[width=3in]{scatter}
\caption{The similarity and distance plot of the training data.
The symbol represents the score, which ranges from 0 to 3.}
\label{fig:scatter}
\end{figure}

% the criteria that were found
From our training data,
the following criteria have been obtained that maximizes the F$_1$ score:

Criteria to find samples with score of 3 (``positive''):
\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
\\ \text{(F$_1$-score: 0.741313)} \end{gather*}

Criteria to find samples with score of 0 (``negative''):
\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
\\ \text{(F$_1$-score: 0.725389)}\end{gather*}

Note that these constant values can vary from project to project, and thus is not a universal constant.

% run result

Running our model against the training data gives us the result displayed in the following table.
In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.

\begin{center}
\begin{tabular}{|r|rrrr|}
\hline
& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
\hline
Negative & 69 & 23 & 7 & 6 \\
Neither & 12 & 24 & 20 & 20 \\
Overlap & 1 & 1 & 0 & 1 \\
Positive & 4 & 13 & 24 & 95 \\
\hline
\end{tabular}
\end{center}

As expected, most comments classified as \emph{negative} have score of 0 and 1,
while most \emph{positive} comments have score of 2 and 3.
However, some comments in every score were lost and classified as \emph{neither}.

% cross validation result
